Self Regulation Ontology Retest Data Report

### 2018-01-24 code/SRO_Report.Rmd
updated pipeline notes and analyses for new notebook

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-17-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-17-2018/'
```

@@

```{r}
hddm_refits <- read.csv(paste'/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')

>>>>

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_01-22-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_01-23-2018/'
```

@@

```{r}
hddm_refits <- read.csv(paste0('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/hddm_refits_exhaustive.csv')
